---
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message = FALSE  )
```

```{r}
library(tidyverse)
library(ggridges)
library(here)
theme_set(theme_minimal())

```

# Simple Parametrization 

- No review

- No metareview

- No harm from kludges

- New Developments Rate: 1

Pure Strategiess:

- Developer 1: Dev: Kludgy/Rev: Careful (does not matter)/Meta: Accurate (does not matter) 

- Developer 2: Dev: Diligent/Rev: Careful (does not matter)/Meta: Accurate (does not matter) 

- Developer 3: Dev: Diligent/Rev: Careful (does not matter)/Meta: Accurate (does not matter) 


## 500 simulation steps 


Estimated time for 30 repetitions of $8^3$ combinations: 12 min per parametrization, 25h (125 parametrizations)


### 30 repetitions

```{r}

plot_abs <- function(results_pre, n, replications ){
  
  results <- map_df(
    .x = 1:replications,
    .f = ~{
      chosen_executions <- sample(x = 1:30, size = n)    
      results_pre %>%  filter(
        execution %in% chosen_executions
      ) %>% 
        mutate(rep = .x)
    }
  )  
  
  ggplot(results,
      aes(
        y = dev,
        x = merges
      )
     ) +
    geom_density_ridges(
      jittered_points = TRUE,
      alpha = 0.2,
      point_alpha = 0.7,
      point_size = 0.7
    ) +
    facet_wrap(
      ~rep,
      ncol = 3
    ) +
    theme(
      legend.position = "top" 
    ) +
    ggtitle(
      str_glue("Merges by developer. {n} repetitions")
    )
}



plot_diff <- function(results_pre, n, replications){
  
  results_diff <-  tibble(
    diff_type = c(
      "Dev_1 - Dev2",
      "Dev_1 - Dev3",
      "Dev_2 - Dev3"
    ),
    minuend_dev = c("Dev_1", "Dev_1", "Dev_2"),
    subtrahend_dev = c("Dev_2", "Dev_3", "Dev_3")
  ) %>% 
    crossing(
      results_pre %>% select(execution) %>%  distinct()
    ) %>% 
    inner_join(
      results_pre %>% select(execution, dev, merges) %>% rename(minuend = merges),
      by = c("execution", "minuend_dev" = "dev")
    ) %>% 
    inner_join(
      results_pre %>% select(execution, dev, merges) %>% rename(subtrahend = merges),
      by = c("execution", "subtrahend_dev" = "dev")
    ) %>% 
    mutate(
      diff = minuend - subtrahend
    )
  
  
  
  results <- map_df(
    .x = 1:replications,
    .f = ~{
      chosen_executions <- sample(x = 1:30, size = n)    
      results_diff %>%  filter(
        execution %in% chosen_executions
      ) %>% 
        mutate(rep = .x)
    }
  )  
  
  ggplot(results,
      aes(
        y = diff_type,
        x = diff
      )
     ) +
    geom_density_ridges(
      jittered_points = TRUE,
      alpha = 0.2,
      point_alpha = 0.7,
      point_size = 0.7
    ) +
    facet_wrap(
      ~rep,
      ncol = 3
    ) +
    theme(
      legend.position = "top" 
    ) +
    geom_vline(
      xintercept = 0,
      color = "darkred",
      size = 1
    ) +
    ggtitle(
      str_glue("Merges (Difference). {n} repetitions")
    )
    


}



```

```{r}
results_pre <- read_rds(here("case_1")) %>% 
  ungroup() %>% 
  mutate(
    dev = str_glue("Dev_{developer}")
  )
```


```{r}
plot_abs(results_pre, n = 30, replications = 1 )

```


```{r}

plot_diff(results_pre, n = 30, replications = 1   )

```


### Samples of 20 repetitions


```{r}
plot_abs(results_pre, n = 20, replications = 6 )

```


```{r}

plot_diff(results_pre, n = 20, replications = 6   )

```

### Samples of 10 repetitions


```{r}
plot_abs(results_pre, n = 10, replications = 12 )

```


```{r}

plot_diff(results_pre, n = 10, replications = 12   )

```

## 300 simulation steps 


Estimated time for 30 repetitions of $8^3$ combinations: 8.5 min per parametrization, 18h (125 parametrizations)



```{r}
results_pre <- read_rds(here("case_2")) %>% 
  ungroup() %>% 
  mutate(
    dev = str_glue("Dev_{developer}")
  )
```


### 30 repetitions

```{r}
plot_abs(results_pre, n = 30, replications = 1 )

```


```{r}

plot_diff(results_pre, n = 30, replications = 1   )

```


### Samples of 20 repetitions

```{r}
plot_abs(results_pre, n = 20, replications = 6 )

```


```{r}

plot_diff(results_pre, n = 20, replications = 6   )

```


### Samples of 10 repetitions


```{r}
plot_abs(results_pre, n = 10, replications = 12 )

```


```{r}

plot_diff(results_pre, n = 10, replications = 12   )

```


## 100 simulation steps

Estimated time for 30 repetitions of $8^3$ combinations: 5.5 min per parametrization, 7.5hh (125 parametrizations)


```{r}
results_pre <- read_rds(here("case_3")) %>% 
  ungroup() %>% 
  mutate(
    dev = str_glue("Dev_{developer}")
  )
```


```{r}
plot_abs(results_pre, n = 30, replications = 1 )

```


```{r}

plot_diff(results_pre, n = 30, replications = 1   )

```


### Samples of 20 repetitions

```{r}
plot_abs(results_pre, n = 20, replications = 6 )

```


```{r}

plot_diff(results_pre, n = 20, replications = 6   )

```


### Samples of 10 repetitions



```{r}
plot_abs(results_pre, n = 10, replications = 12 )

```


```{r}

plot_diff(results_pre, n = 10, replications = 12   )

```





# Complex Parametrization 

- 100% review

- 100% metareview

- No harm from kludges

- New Developments Rate: 1

Pure Strategiess:

- Developer 1: Dev: Kludgy/Rev: Careful/Meta: Accurate

- Developer 2: Dev: Diligent/Rev: Negligent/Meta: Accurate

- Developer 3: Dev: Diligent/Rev: Careful/Meta: Inaccurate



## 500 simulation steps 

Estimated time for 30 repetitions of $8^3$ combinations: 15 min per parametrization, 31h (125 parametrizations)


```{r}
results_pre <- read_rds(here("case_4")) %>% 
  ungroup() %>% 
  mutate(
    dev = str_glue("Dev_{developer}")
  )
```


### 30 repetitions

```{r}
plot_abs(results_pre, n = 30, replications = 1 )

```


```{r}

plot_diff(results_pre, n = 30, replications = 1   )

```


### Samples of 20 repetitions

```{r}
plot_abs(results_pre, n = 20, replications = 6 )

```


```{r}

plot_diff(results_pre, n = 20, replications = 6   )

```


### Samples of 10 repetitions


```{r}
plot_abs(results_pre, n = 10, replications = 12 )

```


```{r}

plot_diff(results_pre, n = 10, replications = 12   )

```




## 800 simulation steps 

Estimated time for 30 repetitions of $8^3$ combinations: 16 min per parametrization, 33.5h (125 parametrizations)


```{r}
results_pre <- read_rds(here("case_5")) %>% 
  ungroup() %>% 
  mutate(
    dev = str_glue("Dev_{developer}")
  )
```


### 30 repetitions

```{r}
plot_abs(results_pre, n = 30, replications = 1 )

```


```{r}

plot_diff(results_pre, n = 30, replications = 1   )

```


### Samples of 20 repetitions

```{r}
plot_abs(results_pre, n = 20, replications = 6 )

```


```{r}

plot_diff(results_pre, n = 20, replications = 6   )

```


### Samples of 10 repetitions


```{r}
plot_abs(results_pre, n = 10, replications = 12 )

```


```{r}

plot_diff(results_pre, n = 10, replications = 12   )

```




# Another Parametrization 

